`r glue::glue('inferCNV results for {params$library_id} with {params$reference_name} reference')`

### 2025-05-14 analyses/infercnv-consensus-cell-type/template-notebooks/SCPCP000015_explore-infercnv-results.Rmd
params not opts

```{r, results = 'asis'}
ref_text <- list(
  "ref_endo" = "endothelial",
  "ref_immune" = "immune",
  "ref_endo-immune" = "endothelial and immune"
)
if (stringr::str_detect(opts$reference_name, "internal")) {
  reference_type_text <- glue::glue("within the `SCPCL000822` library")
} else {
  reference_type_text <- glue::glue("across all `SCPCP000015` libraries")
}

>>>>

```{r, results = 'asis'}
ref_text <- list(
  "ref_endo" = "endothelial",
  "ref_immune" = "immune",
  "ref_endo-immune" = "endothelial and immune"
)
if (stringr::str_detect(params$reference_name, "internal")) {
  reference_type_text <- glue::glue("within the `SCPCL000822` library")
} else {
  reference_type_text <- glue::glue("across all `SCPCP000015` libraries")
}
